---
title: "BabyView Growth Curves"
date: "`r Sys.Date()`"
output: html_document
---

Replicates the CHILDES growth curve pipeline (`docs/data_prep.R`) on BabyView data:
population-level cumulative PPT trajectories and Bayesian Gompertz growth curves
for the same 10 selected function words.

```{r setup, include=FALSE}
library(tidyverse)
library(arrow)
library(feather)
library(brms)
```

# Load Data

```{r load}
babyview_tokens_contract_processed <-
  read_feather("../processed_data/babyview_tokens_contract_processed.feather")
```

# Selected Function Words

```{r function_words}
selected_function_words <- c("the", "and", "no", "not", "i", "you", "can", "have", "do", "it")
function_words <- as.character(intersect(
  selected_function_words,
  unique(as.character(babyview_tokens_contract_processed$word))
))
cat("Function words present in BabyView:\n")
print(function_words)
```

# Population-Level Cumulative PPT

Mirrors `docs/data_prep.R` lines 54–82. Pools all child-speaker tokens per age bin
(no age filter), then takes cumulative sum across age.

```{r pop_traj}
functionword_relfreq_pop <- babyview_tokens_contract_processed %>%
  filter(speaker == "child") %>%
  group_by(word, age) %>%
  summarise(freq = n(), .groups = "drop") %>%
  group_by(age) %>%
  mutate(
    total   = sum(freq),
    relfreq = freq / total,
    ppt     = relfreq * 1000
  ) %>%
  ungroup()

babyview_pop_traj_data <- functionword_relfreq_pop %>%
  filter(word %in% function_words) %>%
  group_by(word) %>%
  arrange(age, .by_group = TRUE) %>%
  mutate(
    cum_freq           = cumsum(freq),
    cum_total          = cumsum(total),
    cumulative_relfreq = cum_freq / cum_total,
    cumulative_ppt     = cumulative_relfreq * 1000
  ) %>%
  ungroup() %>%
  transmute(word, target_child_age = age, cumulative_relfreq, cumulative_ppt)
```

# Per-Word / Per-Speaker Cumulative PPT

Used as input to the Gompertz fitting. Mirrors `docs/data_prep.R` lines 91–99.

```{r word_speaker_relfreq}
functionword_relfreq <- babyview_tokens_contract_processed %>%
  group_by(word, age, speaker) %>%
  summarise(freq = n(), .groups = "drop") %>%
  group_by(speaker, age) %>%
  mutate(total = sum(freq), relfreq = freq / total, ppt = relfreq * 1000) %>%
  group_by(word, speaker) %>%
  arrange(age) %>%
  mutate(
    cum_freq           = cumsum(freq),
    cum_total          = cumsum(total),
    cumulative_relfreq = cum_freq / cum_total,
    cumulative_ppt     = cumulative_relfreq * 1000
  ) %>%
  ungroup()
```

# Gompertz Growth Curves

Same nonlinear Bayesian formula and per-word priors as `docs/data_prep.R`.

```{r gompertz_setup}
gompertz_formula <- bf(
  cumulative_ppt ~ upperAsymptote * exp(-exp(
    ((growthRate * exp(1)) / upperAsymptote) * (lag - age) + 1
  )),
  upperAsymptote ~ 1,
  growthRate     ~ 1,
  lag            ~ 1,
  nl = TRUE
)

get_priors <- function(w) {
  if (w == "and") {
    c(prior(uniform(0, 25), nlpar = "upperAsymptote", lb = 0, ub = 25),
      prior(uniform(0, 5),  nlpar = "growthRate",     lb = 0, ub = 5),
      prior(uniform(0, 72), nlpar = "lag",            lb = 0, ub = 72))
  } else if (w == "the") {
    c(prior(uniform(0, 30), nlpar = "upperAsymptote", lb = 0, ub = 30),
      prior(uniform(0, 10), nlpar = "growthRate",     lb = 0, ub = 10),
      prior(uniform(0, 72), nlpar = "lag",            lb = 0, ub = 72))
  } else if (w == "no") {
    c(prior(uniform(0, 40), nlpar = "upperAsymptote", lb = 0, ub = 40),
      prior(uniform(0, 5),  nlpar = "growthRate",     lb = 0, ub = 5),
      prior(uniform(0, 72), nlpar = "lag",            lb = 0, ub = 72))
  } else if (w == "not") {
    c(prior(uniform(0, 10), nlpar = "upperAsymptote", lb = 0, ub = 10),
      prior(uniform(0, 5),  nlpar = "growthRate",     lb = 0, ub = 5),
      prior(uniform(0, 72), nlpar = "lag",            lb = 0, ub = 72))
  } else {
    c(prior(uniform(0, 30), nlpar = "upperAsymptote", lb = 0, ub = 30),
      prior(uniform(0, 10), nlpar = "growthRate",     lb = 0, ub = 10),
      prior(uniform(0, 72), nlpar = "lag",            lb = 0, ub = 72))
  }
}
```

```{r fit_gompertz, cache=TRUE}
build_gompertz_results <- function(word_vec, traj_tbl, relfreq_tbl) {
  fitted_list <- vector("list", length(word_vec))
  onset_list  <- vector("list", length(word_vec))

  for (i in seq_along(word_vec)) {
    w   <- word_vec[i]
    dat <- relfreq_tbl %>% filter(word == w, speaker == "child")
    ag  <- seq(min(traj_tbl$target_child_age[traj_tbl$word == w], na.rm = TRUE),
               max(traj_tbl$target_child_age[traj_tbl$word == w], na.rm = TRUE),
               length.out = 200)

    if (nrow(dat) < 6) {
      fitted_list[[i]] <- tibble(word = w, target_child_age = ag, fitted = NA_real_)
      next
    }

    priors <- get_priors(w)
    fit <- tryCatch(
      brm(
        formula = gompertz_formula,
        data    = dat,
        prior   = priors,
        iter    = 2000,
        chains  = 4,
        cores   = 1,
        control = list(adapt_delta = 0.9),
        silent  = TRUE,
        refresh = 0
      ),
      error = function(e) { message("brm failed for ", w, ": ", e$message); NULL }
    )

    if (!is.null(fit)) {
      newdata   <- data.frame(age = ag)
      pred_df   <- as.data.frame(fitted(fit, newdata = newdata))
      fitted_list[[i]] <- tibble(word = w, target_child_age = ag,
                                 fitted = as.numeric(pred_df[, "Estimate"]))

      fe <- tryCatch(fixef(fit), error = function(e) NULL)
      if (!is.null(fe) && "lag" %in% rownames(fe)) {
        onset_list[[i]] <- tibble(
          word     = w,
          estimate = fe["lag", "Estimate"],
          q2_5     = fe["lag", "Q2.5"],
          q97_5    = fe["lag", "Q97.5"],
          model    = "bayesian"
        )
      }
    } else {
      fitted_list[[i]] <- tibble(word = w, target_child_age = ag, fitted = NA_real_)
    }
  }

  fitted_df <- bind_rows(fitted_list)
  onset_df  <- bind_rows(onset_list)
  if ("word" %in% names(fitted_df)) fitted_df <- fitted_df %>% mutate(word = as.character(word))
  if ("word" %in% names(onset_df))  onset_df  <- onset_df  %>% mutate(word = as.character(word))
  list(fitted = fitted_df, onset = onset_df)
}

gompertz_results              <- build_gompertz_results(function_words, babyview_pop_traj_data, functionword_relfreq)
babyview_gompertz_fitted_ppt  <- gompertz_results$fitted
babyview_gompertz_onset       <- gompertz_results$onset

# Store fitted values as relative frequency (proportion) to match CHILDES convention
babyview_gompertz_fitted_relfreq <- babyview_gompertz_fitted_ppt %>%
  mutate(fitted = fitted / 1000)
```

# Population Trajectory Plots

Actual cumulative PPT over age (child speech only). Mirrors `plot_population_trajectory()`
in `docs/plots.R`.

```{r pop_traj_plots, fig.width=8, fig.height=4}
for (w in function_words) {
  dat <- babyview_pop_traj_data %>% filter(word == w) %>% arrange(target_child_age)
  if (nrow(dat) == 0) next
  p <- ggplot(dat, aes(x = target_child_age, y = cumulative_ppt)) +
    geom_line(linewidth = 1.2) +
    geom_point(size = 1.6) +
    labs(
      title = paste0('"', w, '" — Population Trajectory (BabyView)'),
      x     = "Age (Months)",
      y     = "Cumulative PPT"
    ) +
    theme_bw()
  print(p)
}
```

# Growth Curve Plots

Actual data (points) overlaid with Gompertz fitted curve (line). Mirrors
`plot_growth_curve()` in `docs/plots.R`.

```{r growth_curve_plots, fig.width=8, fig.height=4}
for (w in function_words) {
  dat   <- babyview_pop_traj_data %>% filter(word == w) %>% arrange(target_child_age)
  curve <- babyview_gompertz_fitted_ppt %>%
    filter(word == w, is.finite(fitted)) %>%
    arrange(target_child_age)

  onset_row <- if ("word" %in% names(babyview_gompertz_onset)) {
    babyview_gompertz_onset %>% filter(word == w)
  } else {
    tibble()
  }
  onset_label <- if (nrow(onset_row) > 0 && is.finite(onset_row$estimate[1])) {
    sprintf("Onset: %.1f mo [%.2f, %.2f]",
            onset_row$estimate[1], onset_row$q2_5[1], onset_row$q97_5[1])
  } else {
    "Onset: not estimated"
  }

  p <- ggplot() +
    geom_point(
      data = dat,
      aes(x = target_child_age, y = cumulative_ppt, color = "Actual Data"),
      size = 1.6
    )

  if (nrow(curve) > 0) {
    p <- p + geom_line(
      data = curve,
      aes(x = target_child_age, y = fitted, color = "Fitted Values"),
      linewidth = 1.6
    )
  }

  p <- p +
    scale_color_manual(
      name   = "Legend",
      values = c("Actual Data" = "#FDB515", "Fitted Values" = "#003262")
    ) +
    labs(
      title    = paste0('"', w, '" — Growth Curve (BabyView)'),
      subtitle = onset_label,
      x        = "Age (Months)",
      y        = "Cumulative Parts Per Thousand"
    ) +
    theme_bw()
  print(p)
}
```

# Onset Estimates

```{r onset_table}
if (nrow(babyview_gompertz_onset) > 0) {
  babyview_gompertz_onset %>%
    arrange(estimate) %>%
    knitr::kable(digits = 2, caption = "Gompertz onset estimates (BabyView)")
} else {
  cat("No onset estimates produced.\n")
}
```

# Save Output

```{r save}
write_feather(babyview_pop_traj_data,
              "../processed_data/babyview_pop_traj_data.feather")
write_feather(babyview_gompertz_fitted_relfreq,
              "../processed_data/babyview_gompertz_fitted_relfreq.feather")
write_feather(babyview_gompertz_onset,
              "../processed_data/babyview_gompertz_onset_estimates.feather")

message("Saved babyview_pop_traj_data, babyview_gompertz_fitted_relfreq, babyview_gompertz_onset_estimates to processed_data/")
```
