---
title: "English Plots (Refactored)"
author: "Masoud Jasbi"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r packages, include=FALSE}
library(tidyverse)
library(feather)
library(brms)
library(ggeffects)
library(ggrepel)
library(grid)
library(gridExtra)
```

# Load Data

```{r processedEnglishTokens}
english_tokens_processed <- read_feather("../processed_data/english_tokens_processed.feather")

english_tokens_contract_processed <-
  read_feather("../processed_data/english_tokens_contract_processed.feather") %>%
  filter(speaker != "child" | age >= 12)
```

# Computing Cumulative Relative Frequencies

## Function vs. Content Words

Here we compute cumulative relative frequencies of function vs. content words by grouping by "syntactic category":

```{r syncategory_relfreq}
syncategory_relfreq <-
  english_tokens_contract_processed %>%
  group_by(syncategory, age, speaker) %>%
  summarise(freq=n()) %>%
  group_by(speaker, age) %>%
  mutate(total=sum(freq), relfreq=freq/sum(freq), pct=relfreq*100) %>%
  group_by(syncategory, speaker) %>%
  arrange(age) %>%
  mutate(cum_freq = cumsum(freq), cum_total= cumsum(total),
         cumulative_relfreq = cumsum(freq)/cumsum(total),
         cumulative_pct=cumulative_relfreq*100)

saveRDS(syncategory_relfreq, "syncategory_relfreq.RDS")
```

## Individual Function Words

Here we compute cumulative relative frequencies for individual function words by grouping by "word":

```{r functionword_relfreq}
functionword_relfreq <-
  english_tokens_contract_processed %>%
  group_by(word, age, speaker) %>%
  summarise(freq=n()) %>%
  group_by(speaker, age) %>%
  mutate(total=sum(freq), relfreq=freq/sum(freq), ppt=relfreq*1000) %>%
  group_by(word, speaker) %>%
  arrange(age) %>%
  mutate(cum_freq = cumsum(freq), cum_total= cumsum(total),
         cumulative_relfreq = cumsum(freq)/cumsum(total),
         cumulative_ppt=cumulative_relfreq*1000)

saveRDS(functionword_relfreq, "functionword_relfreq.RDS")
```

## Function Word Semantic Categories

Here we compute cumulative relative frequencies by semantic categories we have created. However, we have not planned any analyses of these yet.

```{r wordcategory_relfreq}
wordcategory_relfreq <-
  english_tokens_contract_processed %>%
  group_by(word_category, age, speaker) %>%
  summarise(freq=n()) %>%
  group_by(speaker, age) %>%
  mutate(total=sum(freq), relfreq=freq/sum(freq), ppt=relfreq*1000) %>%
  group_by(word_category, speaker) %>%
  arrange(age) %>%
  mutate(cum_freq = cumsum(freq), cum_total= cumsum(total),
         cumulative_relfreq = cumsum(freq)/cumsum(total))

saveRDS(wordcategory_relfreq, "wordcategory_relfreq.RDS")
```

## Function Word Syntactic Categories

We have not yet looked at the emergence of different syntactic categories.

# Plots and Growth Curves

## Content vs. Function Word Production

The graph below shows percent word category (content vs. function word) in each monthly bin during the development of the child for parents and children.

```{r content_func_plot}
p <- syncategory_relfreq %>%
  ggplot(aes(age, pct)) +
  geom_point() +
  facet_grid(speaker~syncategory) +
  theme_bw()

p
ggsave("../pics/content_func.pdf", plot=p)
saveRDS(p, "../plots/content_func_plot.RDS")
```

```{r function_words_growth_model, include=FALSE}
function_words_lagModel <- brm(
  bf(pct  ~ upperAsymptote * exp(-exp(((growthRate*exp(1))/upperAsymptote)*(lag-age)+1)),
     upperAsymptote ~ 1,
     growthRate ~ 1,
     lag ~ 1,
     nl = TRUE),
  data = filter(syncategory_relfreq, syncategory=="Function", speaker=="child"),
  prior = c(
    prior(uniform(0, 100), nlpar = "upperAsymptote", lb = 0, ub = 100),
    prior(uniform(0, 10), nlpar = "growthRate", lb = 0, ub = 10),
    prior(uniform(0, 72), nlpar = "lag", lb = 0, ub = 72)
  ),
  file = "../modeling/function_word_lagModel",
  iter = 10000)
```

```{r function_word_predictions}
function_words_predictions <- as.data.frame(fitted(function_words_lagModel))

function_words_childdata <- filter(syncategory_relfreq, syncategory=="Function", speaker=="child")
function_words_childdata$predictions <- function_words_predictions[, "Estimate"]

saveRDS(function_words_childdata, "../processed_data/function_words_childdata.RDS")
```

```{r function_words_plot}
function_words_plot <-
  ggplot(function_words_childdata, aes(x = age, y = pct)) +
  geom_point(aes(color = "Actual Data"), size = 2) +
  geom_line(aes(y = predictions, color = "Fitted Values"), size = 1) +
  scale_color_manual(name = "Legend", values = c("Actual Data" = "black", "Fitted Values" = "blue")) +
  theme_bw() + labs(title="Function Words", x="Child Age (Month)", y="Percent") +
  theme(legend.position = "none") +
  theme(
    plot.title = element_text(size = 20, hjust = 0.5),
    axis.title.x = element_text(size = 16),
    axis.title.y = element_text(size = 16),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.text  = element_text(size = 12)
  )
```

## Distribution of Individual Function Words

### Helper Function

```{r process_word_fn}
process_word <- function(word, model_file, upper_asymptote,
                          gr_prior, gr_ub, adapt_delta = NULL) {
  w <- word  # local alias avoids collision with dplyr's `word` column name

  # Comparison plot (child + adult, faceted)
  p_comparison <- functionword_relfreq %>%
    filter(word == w) %>%
    ggplot(aes(age, cumulative_ppt)) +
    geom_point() +
    facet_grid(.~speaker) +
    theme_bw() +
    xlab("Age (Months)") + ylab("Cumulative Parts Per Thousand")
  print(p_comparison)

  # Build priors using prior() via eval(parse()) so the expression is identical
  # to what the original hard-coded calls produce, preserving the brms model hash
  # and allowing cached .rds fits to load without refitting.
  priors <- c(
    eval(parse(text = paste0(
      'prior(uniform(0, ', upper_asymptote, '), nlpar = "upperAsymptote", lb = 0, ub = ', upper_asymptote, ')'))),
    eval(parse(text = paste0(
      'prior(uniform(0, ', gr_prior, '), nlpar = "growthRate", lb = 0, ub = ', gr_ub, ')'))),
    prior(uniform(0, 72), nlpar = "lag", lb = 0, ub = 72)
  )

  # Optional adapt_delta: only pass control when specified
  ctrl <- if (!is.null(adapt_delta) && !is.na(adapt_delta))
    list(adapt_delta = adapt_delta) else NULL

  lag_model <- brm(
    bf(cumulative_ppt ~ upperAsymptote * exp(-exp(((growthRate*exp(1))/upperAsymptote)*(lag-age)+1)),
       upperAsymptote ~ 1,
       growthRate ~ 1,
       lag ~ 1,
       nl = TRUE),
    data = filter(functionword_relfreq, word == w, speaker == "child"),
    prior = priors,
    control = ctrl,
    file = model_file,
    iter = 10000
  )

  # Predictions and save
  child_data <- filter(functionword_relfreq, word == w, speaker == "child")
  child_data$predictions <- as.data.frame(fitted(lag_model, newdata = child_data))[, "Estimate"]
  saveRDS(child_data,
          paste0("../processed_data/",
                 gsub("_lagModel$", "", basename(model_file)),
                 "_childdata.RDS"))

  # Smooth fitted curve over 200 age points for word_model_db
  ag <- seq(min(child_data$age), max(child_data$age), length.out = 200)
  fitted_vals <- as.data.frame(fitted(lag_model, newdata = data.frame(age = ag)))[, "Estimate"]
  fitted_curve_tbl <- tibble(age = ag, fitted_ppt = fitted_vals) %>%
    filter(is.finite(fitted_ppt))

  # Prediction plot: capitalize first letter, but keep special forms unchanged
  word_title <- if (word %in% c("n't", "'m")) word else
    paste0(toupper(substring(word, 1, 1)), substring(word, 2))

  word_plot <- ggplot(child_data, aes(x = age, y = cumulative_ppt)) +
    geom_point(aes(color = "Actual Data"), size = 2) +
    geom_line(aes(y = predictions, color = "Fitted Values"), size = 1) +
    scale_color_manual(name = "Legend",
                       values = c("Actual Data" = "black", "Fitted Values" = "blue")) +
    theme_bw() +
    labs(title = word_title, x = "", y = "") +
    theme(legend.position = "none",
          plot.title = element_text(size = 20, hjust = 0.5),
          axis.title.x = element_text(size = 16),
          axis.title.y = element_text(size = 16),
          axis.text.x  = element_text(size = 14),
          axis.text.y  = element_text(size = 14),
          legend.title = element_text(size = 14),
          legend.text  = element_text(size = 12))
  print(word_plot)

  # age_of_production row as character vector (matches original rbind convention)
  aop_row  <- c(word, round(fixef(lag_model)[3, ], 1))
  aop_nums <- as.numeric(round(fixef(lag_model)[3, ], 1))

  rm(lag_model)
  gc()

  invisible(list(plot = word_plot, aop_row = aop_row,
                 child_data = child_data, fitted_curve = fitted_curve_tbl,
                 aop_nums = aop_nums))
}
```

### Word Parameters Table

One row per unique word, in semantic-category order matching the original. Model file paths are
preserved exactly so brm loads cached fits instead of refitting.

```{r word_params}
word_params <- tribble(
  ~word,       ~category,                      ~model_file,                          ~upper_asymptote, ~gr_prior, ~gr_ub, ~adapt_delta,
  # Connectives
  "no",        "Connectives",                  "../modeling/neg_no_lagModel",         40,    5,   5,   NA,
  "yes",       "Connectives",                  "../modeling/yes_lagModel",            15,    5,   5,   NA,
  "not",       "Connectives",                  "../modeling/neg_not_lagModel",        10,    5,   5,   NA,
  "n't",       "Connectives",                  "../modeling/neg_nt_lagModel",         15,    5,   5,   NA,
  "and",       "Connectives",                  "../modeling/and_lagModel",            25,    5,   5,   NA,
  "or",        "Connectives",                  "../modeling/or_lagModel",              2,   10,  10,   NA,
  "if",        "Connectives",                  "../modeling/if_lagModel",              2,    5,   5,   NA,
  "but",       "Connectives",                  "../modeling/but_lagModel",             5,   10,  10,   NA,
  "because",   "Connectives",                  "../modeling/because_lagModel",         5,   10,  10,   NA,
  "unless",    "Connectives",                  "../modeling/unless_lagModel",          0.03, 10,  10,   NA,
  # Definites and Demonstratives
  "the",       "Definites and Demonstratives", "../modeling/the_lagModel",            30,   10,  10,   NA,
  "a",         "Definites and Demonstratives", "../modeling/a_lagModel",              40,    5,   5,   NA,
  "this",      "Definites and Demonstratives", "../modeling/this_lagModel",           20,    5,   5,   0.9,
  "that",      "Definites and Demonstratives", "../modeling/that_lagModel",           30,   10,  10,   0.95,
  "these",     "Definites and Demonstratives", "../modeling/these_lagModel",           3,   10,  10,   NA,
  "those",     "Definites and Demonstratives", "../modeling/those_lagModel",           2,    5,   5,   0.9,
  # Wh Words
  "what",      "Wh Words",                     "../modeling/what_lagModel",           20,   10,  10,   0.9,
  "who",       "Wh Words",                     "../modeling/who_lagModel",            10,    5,   5,   NA,
  "when",      "Wh Words",                     "../modeling/when_lagModel",            5,   10,  10,   NA,
  "where",     "Wh Words",                     "../modeling/where_lagModel",          10,   10,  10,   NA,
  "why",       "Wh Words",                     "../modeling/why_lagModel",            10,   10,  10,   NA,
  "how",       "Wh Words",                     "../modeling/how_lagModel",             5,   10,  10,   0.9,
  "whose",     "Wh Words",                     "../modeling/whose_lagModel",           1,    5,   5,   0.95,
  # Modals
  "can",       "Modals",                       "../modeling/can_lagModel",            20,    5,   5,   NA,
  "could",     "Modals",                       "../modeling/could_lagModel",           5,    5,   5,   NA,
  "need",      "Modals",                       "../modeling/need_lagModel",            5,   10,  10,   NA,
  "maybe",     "Modals",                       "../modeling/maybe_lagModel",           1,   10,  10,   0.95,
  "might",     "Modals",                       "../modeling/might_lagModel",           1,   10,  10,   0.95,
  "must",      "Modals",                       "../modeling/must_lagModel",            1,   10,  10,   0.9,
  "should",    "Modals",                       "../modeling/should_lagModel",          1,   10,  10,   0.98,
  # Individual Quantifiers
  "all",       "Individual Quantifiers",       "../modeling/all_lagModel",            10,   10,  10,   NA,
  "some",      "Individual Quantifiers",       "../modeling/some_lagModel",           10,   10,  10,   NA,
  "both",      "Individual Quantifiers",       "../modeling/both_lagModel",            0.5, 10,  10,   0.99,
  "each",      "Individual Quantifiers",       "../modeling/each_lagModel",            1,   10,  10,   0.9,
  "most",      "Individual Quantifiers",       "../modeling/most_lagModel",            0.5, 10,  10,   0.95,
  "every",     "Individual Quantifiers",       "../modeling/every_lagModel",           1,   10,  10,   0.95,
  "many",      "Individual Quantifiers",       "../modeling/many_lagModel",            1,    5,   5,   0.9,
  "none",      "Individual Quantifiers",       "../modeling/none_lagModel",            0.5, 10,  10,   NA,
  # Temporal Quantifiers
  "always",    "Temporal Quantifiers",         "../modeling/always_lagModel",          1,   10,  10,   NA,
  "sometimes", "Temporal Quantifiers",         "../modeling/sometimes_lagModel",       1,   10,  10,   NA,
  "usually",   "Temporal Quantifiers",         "../modeling/usually_lagModel",         1,    5,   5,   NA,
  "never",     "Temporal Quantifiers",         "../modeling/never_lagModel",           1,    5,   5,   0.99,
  "once",      "Temporal Quantifiers",         "../modeling/once_lagModel",            1,    5,   5,   0.9,
  # Temporals
  "before",    "Temporals",                    "../modeling/before_lagModel",          1,    5,   5,   NA,
  "after",     "Temporals",                    "../modeling/after_lagModel",           1,    5,   5,   NA,
  "then",      "Temporals",                    "../modeling/then_lagModel",            5,    5,   5,   NA,
  "until",     "Temporals",                    "../modeling/until_lagModel",           1,   10,  10,   NA,
  "while",     "Temporals",                    "../modeling/while_lagModel",           1,    5,   5,   NA,
  # Comparatives
  "more",      "Comparatives",                 "../modeling/more_lagModel",           10,   10,  10,   NA,
  "less",      "Comparatives",                 "../modeling/less_lagModel",            1,    5,   5,   NA,
  "much",      "Comparatives",                 "../modeling/much_lagModel",            1,   10,  10,   0.98,
  # Number Words
  "one",       "Number Words",                 "../modeling/one_lagModel",            12,    5,   5,   0.9,
  "two",       "Number Words",                 "../modeling/two_lagModel",            12,    5,   5,   0.9,
  "three",     "Number Words",                 "../modeling/three_lagModel",           3,    5,   5,   0.95,
  "four",      "Number Words",                 "../modeling/four_lagModel",            2,    5,   5,   0.9,
  "five",      "Number Words",                 "../modeling/five_lagModel",            2,    5,   5,   0.9,
  "six",       "Number Words",                 "../modeling/six_lagModel",             1,    5,   5,   0.9,
  "seven",     "Number Words",                 "../modeling/seven_lagModel",           1,    5,   5,   0.9,
  "eight",     "Number Words",                 "../modeling/eight_lagModel",           1,    5,   5,   0.98,
  "nine",      "Number Words",                 "../modeling/nine_lagModel",            1,    5,   5,   0.95,
  "ten",       "Number Words",                 "../modeling/ten_lagModel",             1,    5,   5,   0.98,
  # Ordinals
  "first",     "Ordinals",                     "../modeling/first_lagModel",           1,    5,   5,   0.9,
  "last",      "Ordinals",                     "../modeling/last_lagModel",            1,    5,   5,   0.9,
  "second",    "Ordinals",                     "../modeling/second_lagModel",          1,    5,   5,   0.9,
  # Additives
  "again",     "Additives",                    "../modeling/again_lagModel",           3,   10,  10,   0.9,
  "too",       "Additives",                    "../modeling/too_lagModel",             5,   10,  10,   0.98,
  "also",      "Additives",                    "../modeling/also_lagModel",            1,    5,   5,   0.95,
  "another",   "Additives",                    "../modeling/another_lagModel",         5,    5,   5,   0.95,
  "still",     "Additives",                    "../modeling/still_lagModel",           1,    5,   5,   0.95,
  "other",     "Additives",                    "../modeling/other_lagModel",           5,   10,  10,   0.95,
  # Negative Polarity Items
  "any",       "Negative Polarity Items",      "../modeling/any_lagModel",             1,   10,  10,   NA,
  "yet",       "Negative Polarity Items",      "../modeling/yet_lagModel",             1,    5,   5,   NA,
  "ever",      "Negative Polarity Items",      "../modeling/ever_lagModel",            1,   10,  10,   NA,
  "anyone",    "Negative Polarity Items",      "../modeling/anyone_lagModel",          1,    5,   5,   0.98,
  "anything",  "Negative Polarity Items",      "../modeling/anything_lagModel",        1,    5,   5,   0.9,
  "anywhere",  "Negative Polarity Items",      "../modeling/anywhere_lagModel",        1,    5,   5,   NA,
  "anyway",    "Negative Polarity Items",      "../modeling/anyway_lagModel",          1,    5,   5,   0.95,
  # Exclusives
  "only",      "Exclusives",                   "../modeling/only_lagModel",            1,    5,   5,   0.95,
  "just",      "Exclusives",                   "../modeling/just_lagModel",            5,   10,  10,   0.95,
  # Locatives
  "here",      "Locatives",                    "../modeling/here_lagModel",           10,   10,  10,   0.95,
  "there",     "Locatives",                    "../modeling/there_lagModel",          30,   10,  10,   0.95,
  "up",        "Locatives",                    "../modeling/up_lagModel",             10,   10,  10,   NA,
  "on",        "Locatives",                    "../modeling/on_lagModel",             20,   10,  10,   0.9,
  "in",        "Locatives",                    "../modeling/in_lagModel",             20,   10,  10,   NA,
  "out",       "Locatives",                    "../modeling/out_lagModel",             6,   10,  10,   0.9,
  "down",      "Locatives",                    "../modeling/down_lagModel",           10,   10,  10,   0.9,
  "into",      "Locatives",                    "../modeling/into_lagModel",            1,   10,  10,   0.9,
  "under",     "Locatives",                    "../modeling/under_lagModel",           1,   10,  10,   0.9,
  "over",      "Locatives",                    "../modeling/over_lagModel",            5,   10,  10,   0.9,
  "behind",    "Locatives",                    "../modeling/behind_lagModel",          1,   10,  10,   0.9,
  "near",      "Locatives",                    "../modeling/near_lagModel",            1,    5,   5,   0.9,
  "onto",      "Locatives",                    "../modeling/onto_lagModel",            1,   10,  10,   0.9,
  # Other
  "either",    "Other",                        "../modeling/either_lagModel",          1,   10,  10,   0.9,
  "else",      "Other",                        "../modeling/else_lagModel",            1,    5,   5,   0.9,
  "almost",    "Other",                        "../modeling/almost_lagModel",          1,   10,  10,   0.9,
  "already",   "Other",                        "../modeling/already_lagModel",         1,    5,   5,   0.95,
  "except",    "Other",                        "../modeling/except_lagModel",          1,   10,  10,   0.9,
  "for",       "Other",                        "../modeling/for_lagModel",             6,    5,   5,   0.9,
  "from",      "Other",                        "../modeling/from_lagModel",            5,   10,  10,   0.9,
  "to",        "Other",                        "../modeling/to_lagModel",             20,   10,  10,   0.9,
  "by",        "Other",                        "../modeling/by_lagModel",              1,   10,  10,   0.9,
  "very",      "Other",                        "../modeling/very_lagModel",            2,   10,  10,   0.9,
  "with",      "Other",                        "../modeling/with_lagModel",            5,   10,  10,   0.9,
  "without",   "Other",                        "../modeling/without_lagModel",         1,    5,   5,   0.9,
  "instead",   "Other",                        "../modeling/instead_lagModel",         1,    5,   5,   0.9,
  "such",      "Other",                        "../modeling/such_lagModel",            1,    5,   5,   0.9,
  "about",     "Other",                        "../modeling/about_lagModel",           5,   10,  10,   0.9,
  # Pronouns
  "mine",      "Pronouns",                     "../modeling/mine_lagModel",            5,   10,  10,   0.9,
  "me",        "Pronouns",                     "../modeling/me_lagModel",             10,   10,  10,   0.9,
  "i",         "Pronouns",                     "../modeling/I_lagModel",              50,   10,  10,   0.9,
  "you",       "Pronouns",                     "../modeling/you_lagModel",            50,   10,  10,   0.9,
  "your",      "Pronouns",                     "../modeling/your_lagModel",           10,   10,  10,   0.9,
  "we",        "Pronouns",                     "../modeling/we_lagModel",             10,   10,  10,   0.9,
  "our",       "Pronouns",                     "../modeling/our_lagModel",             1,   10,  10,   0.9,
  "ours",      "Pronouns",                     "../modeling/ours_lagModel",            1,   10,  10,   0.9,
  "she",       "Pronouns",                     "../modeling/she_lagModel",             6,   10,  10,   0.9,
  "her",       "Pronouns",                     "../modeling/her_lagModel",             6,   10,  10,   0.9,
  "he",        "Pronouns",                     "../modeling/he_lagModel",             10,   10,  10,   0.9,
  "his",       "Pronouns",                     "../modeling/his_lagModel",            10,   10,  10,   0.9,
  "they",      "Pronouns",                     "../modeling/they_lagModel",           10,   10,  10,   0.9,
  "their",     "Pronouns",                     "../modeling/their_lagModel",          10,   10,  10,   0.9,
  "it",        "Pronouns",                     "../modeling/it_lagModel",             50,   10,  10,   0.9,
  "its",       "Pronouns",                     "../modeling/its_lagModel",             1,   10,  10,   0.9,
  "'m",        "Pronouns",                     "../modeling/m_lagModel",              10,   10,  10,   0.9,
  # Auxiliaries
  "am",        "Auxiliaries",                  "../modeling/am_lagModel",              1,   10,  10,   0.9,
  "is",        "Auxiliaries",                  "../modeling/is_lagModel",             50,   10,  10,   0.9,
  "are",       "Auxiliaries",                  "../modeling/are_lagModel",            10,   10,  10,   0.9,
  "was",       "Auxiliaries",                  "../modeling/was_lagModel",            10,   10,  10,   0.9,
  "were",      "Auxiliaries",                  "../modeling/were_lagModel",            2,   10,  10,   0.9,
  "do",        "Auxiliaries",                  "../modeling/do_lagModel",             50,   10,  10,   0.9,
  "does",      "Auxiliaries",                  "../modeling/does_lagModel",           10,   10,  10,   0.9
)
```

### Initialize Storage

```{r init_storage}
word_plots <- list()

if (file.exists("../processed_data/word_model_db.RDS")) {
  word_model_db <- readRDS("../processed_data/word_model_db.RDS")
  age_of_production <- word_model_db %>%
    select(word, Estimate = aop_estimate, Est.Error = aop_err,
           Q2.5 = aop_q2_5, Q97.5 = aop_q97_5) %>%
    as.data.frame(stringsAsFactors = FALSE)
} else {
  word_model_db <- tibble(
    word         = character(),
    child_data   = list(),
    fitted_curve = list(),
    aop_estimate = numeric(),
    aop_err      = numeric(),
    aop_q2_5     = numeric(),
    aop_q97_5    = numeric()
  )
  age_of_production <- NULL
}

run_category <- function(cat_name) {
  cat_words <- filter(word_params, category == cat_name)
  for (i in seq_len(nrow(cat_words))) {
    p <- cat_words[i, ]
    if (p$word %in% word_model_db$word) next
    result <- process_word(p$word, p$model_file, p$upper_asymptote,
                           p$gr_prior, p$gr_ub, p$adapt_delta)
    word_plots[[p$word]]  <<- result$plot
    age_of_production     <<- rbind(age_of_production, result$aop_row)
    word_model_db         <<- bind_rows(word_model_db, tibble(
      word         = p$word,
      child_data   = list(result$child_data),
      fitted_curve = list(result$fitted_curve),
      aop_estimate = result$aop_nums[1],
      aop_err      = result$aop_nums[2],
      aop_q2_5     = result$aop_nums[3],
      aop_q97_5    = result$aop_nums[4]
    ))
    saveRDS(word_model_db, "../processed_data/word_model_db.RDS")
  }
}
```

### Connectives

```{r connectives, message=FALSE, warning=FALSE}
run_category("Connectives")
```

### Definites and Demonstratives

```{r definites, message=FALSE, warning=FALSE}
run_category("Definites and Demonstratives")
```

### Wh Words

```{r wh_words, message=FALSE, warning=FALSE}
run_category("Wh Words")
```

### Modals

```{r modals, message=FALSE, warning=FALSE}
run_category("Modals")
```

### Individual Quantifiers

```{r individual_quantifiers, message=FALSE, warning=FALSE}
run_category("Individual Quantifiers")
```

### Temporal Quantifiers

```{r temporal_quantifiers, message=FALSE, warning=FALSE}
run_category("Temporal Quantifiers")
```

### Temporals

```{r temporals, message=FALSE, warning=FALSE}
run_category("Temporals")
```

### Comparatives

```{r comparatives, message=FALSE, warning=FALSE}
run_category("Comparatives")
```

### Number Words

```{r number_words, message=FALSE, warning=FALSE}
run_category("Number Words")
```

### Ordinals

```{r ordinals, message=FALSE, warning=FALSE}
run_category("Ordinals")
```

### Additives

```{r additives, message=FALSE, warning=FALSE}
run_category("Additives")
```

### Negative Polarity Items

```{r negative_polarity, message=FALSE, warning=FALSE}
run_category("Negative Polarity Items")
```

### Exclusives

```{r exclusives, message=FALSE, warning=FALSE}
run_category("Exclusives")
```

### Locatives

```{r locatives, message=FALSE, warning=FALSE}
run_category("Locatives")
```

### Other

```{r other, message=FALSE, warning=FALSE}
run_category("Other")
```

### Pronouns

```{r pronouns, message=FALSE, warning=FALSE}
run_category("Pronouns")
```

### Auxiliaries

```{r auxiliaries, message=FALSE, warning=FALSE}
run_category("Auxiliaries")
```

### Finalize Age of Production Table

```{r finalize_aop}
age_of_production <- as.data.frame(age_of_production, stringsAsFactors = FALSE)
colnames(age_of_production) <- c("word", "Estimate", "Est.Error", "Q2.5", "Q97.5")
rownames(age_of_production) <- NULL
```

```{r save_word_model_db}
saveRDS(word_model_db, "../processed_data/word_model_db.RDS")
```

# Collection of Some Plots

```{r collection_plots}
library(gridExtra)

grid.arrange(
  word_plots[["me"]], word_plots[["more"]], word_plots[["what"]], word_plots[["the"]],
  word_plots[["some"]], word_plots[["and"]], word_plots[["can"]], word_plots[["in"]],
  layout_matrix = rbind(c(1, 2), c(3, 4), c(5, 6), c(7, 8)),
  bottom = textGrob("Age (Months)", gp = gpar(fontsize = 13)),
  left   = textGrob("Words (Per Thousand)", gp = gpar(fontsize = 13), rot = 90))

grid.arrange(
  word_plots[["if"]], word_plots[["any"]], word_plots[["can"]], word_plots[["n't"]],
  word_plots[["up"]], word_plots[["who"]], word_plots[["just"]], word_plots[["all"]],
  layout_matrix = rbind(c(1, 2), c(3, 4), c(5, 6), c(7, 8)),
  bottom = textGrob("Age (Months)", gp = gpar(fontsize = 13)),
  left   = textGrob("Words (Per Thousand)", gp = gpar(fontsize = 13), rot = 90))
```

# Age of Production Plot

```{r age_of_production_process}
age_of_production <-
  age_of_production %>%
  mutate(
    Estimate  = as.numeric(Estimate),
    Est.Error = as.numeric(Est.Error),
    Q2.5      = as.numeric(Q2.5),
    Q97.5     = as.numeric(Q97.5)
  ) %>%
  mutate(word = fct_reorder(word, Estimate))

saveRDS(age_of_production, "../processed_data/age_of_production.RDS")
```

```{r onset_age_plot}
age_of_production <- readRDS("../processed_data/age_of_production.RDS")

functionword_onsetage_plot <-
  age_of_production %>%
  mutate(word = fct_reorder(word, Estimate)) %>%
  ggplot(aes(x=Estimate, y=word)) +
  geom_pointrange(aes(xmin = Q2.5, xmax = Q97.5)) +
  theme_bw() +
  theme(axis.text.y = element_text(size = 12), xlab="age") +
  scale_x_continuous(breaks = seq(0, 72, by = 3)) +
  labs(x = "Age (Months)", y="") +
  theme(text = element_text(size = 12))

functionword_onsetage_plot
```

# Wordbank MB-CDI Function Word Trajectories

## English Function Word Trajectory Plots

```{r cdi_load}
cdi_data <-
  read_csv("../raw_data/wordbank_functionword_trajectories.csv") %>%
  gather("word", "proportion", a:how)

#write_csv(cdi_data, "../processed_data/cdi_functionwords.csv")
```

```{r functionWordPlots}
cdi_data <- read_csv("../processed_data/cdi_functionwords.csv")

last_points <- cdi_data %>%
  group_by(word) %>%
  slice_max(order_by = age, n = 1)

ggplot(cdi_data, aes(x = age, y = proportion, colour = word)) +
  geom_line() +
  geom_text_repel(data = last_points, aes(label = word),
                  nudge_x = 1,
                  direction = "y",
                  color = "black",
                  show.legend = FALSE) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1)) +
  theme_bw() +
  theme(axis.text = element_text(size = 14), legend.position = "none") +
  labs(x = "Age (Months)", y = "Proportion")
```

```{r wordbankr_load}
library(wordbankr)
```

```{r wordbank_api}
eng_ws_data <- get_instrument_data(language = "English (American)",
                                   form = "WS",
                                   administration_info = TRUE,
                                   item_info = TRUE)

wordbank_df <- eng_ws_data %>% select(item_definition, age, produces, child_id)
wordbank_df$item_definition <- trimws(tolower(wordbank_df$item_definition))

func_wordbank <- wordbank_df[wordbank_df$item_definition %in% function_words, ]

word_proportions <- func_wordbank %>%
  group_by(item_definition, age) %>%
  summarise(
    total_children = n_distinct(child_id),
    children_producing = sum(produces == TRUE),
    proportion = children_producing / total_children,
    .groups = 'drop'
  )

ggplot(word_proportions, aes(x = age, y = proportion, color = item_definition)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
  labs(
    title = "Proportion of Children Producing Each Word by Age",
    x = "Age (months)",
    y = "Proportion of Children",
    color = "Word"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, hjust = 0.5),
    legend.position = "right",
    legend.text = element_text(size = 8),
    legend.title = element_text(size = 10),
    legend.key.size = unit(0.5, "cm")
  ) +
  guides(color = guide_legend(ncol = 2))
```

## Onset Age of Production Estimates

```{r cdi_onset_age}
CDI_onset_age <-
  cdi_data %>%
  group_by(word) %>%
  summarise(
    age_above_0.1  = min(age[proportion >= 0.1],  na.rm = TRUE),
    age_above_0.15 = min(age[proportion >= 0.15], na.rm = TRUE),
    age_above_0.2  = min(age[proportion >= 0.2],  na.rm = TRUE)
  )
```

```{r cdi_onset_plot}
CDI_onset_age %>%
  ggplot(aes(x = age_above_0.15, y = reorder(word, age_above_0.15))) +
  geom_pointrange(aes(xmin = age_above_0.1, xmax = age_above_0.2)) +
  theme_bw() +
  theme(axis.text.y = element_text(size = 14), xlab = "age") +
  labs(x = "Age (Months)", y = "") +
  scale_x_continuous(breaks = seq(min(CDI_onset_age$age_above_0.15),
                                  max(CDI_onset_age$age_above_0.15), by = 1))
```
