---
title: "CDI Validation of CHILDES Age of Production Estimates"
author: ""
date: "`r Sys.Date()`"
output: html_document
---

```{r packages, include=FALSE}
library(tidyverse)
library(ggrepel)
library(broom)
```

# Load Data

CHILDES-derived onset-of-production estimates (Gompertz growth-curve `lag`
parameter, fit per word on cumulative child production frequency):

```{r loadChildes}
age_of_production <- readRDS("../processed_data/age_of_production.RDS")

age_of_production <- age_of_production %>%
  mutate(word = as.character(word))

age_of_production
```

CDI (Wordbank) parent-report production data:

```{r loadCDI}
cdi_data <- read_csv("../processed_data/cdi_functionwords.csv", show_col_types = FALSE)

cdi_data
```

# Compute CDI Onset Ages

For each word, the earliest age (months) at which the proportion of children
reported to produce it crosses 0.1 / 0.15 / 0.2.

```{r cdiOnsetAge}
CDI_onset_age <- cdi_data %>%
  group_by(word) %>%
  summarise(
    age_above_0.1  = min(age[proportion >= 0.1],  na.rm = TRUE),
    age_above_0.15 = min(age[proportion >= 0.15], na.rm = TRUE),
    age_above_0.2  = min(age[proportion >= 0.2],  na.rm = TRUE)
  )

CDI_onset_age
```

# Normalize Word Tokens and Join

CDI and CHILDES tokenize a few words differently. We apply only unambiguous
one-to-one mappings; contractions (`'m`/`am`, `n't`/`don't`) are structurally
different tokens on the CHILDES side and are left unmatched rather than
force-mapped.

```{r normalizeJoin}
CDI_onset_age_norm <- CDI_onset_age %>%
  mutate(word = recode(word,
    "can (auxiliary)" = "can",
    "inside/in"        = "in"
  ))

comparison <- inner_join(age_of_production, CDI_onset_age_norm, by = "word")

childes_unmatched <- setdiff(age_of_production$word, CDI_onset_age_norm$word)
cdi_unmatched     <- setdiff(CDI_onset_age_norm$word, age_of_production$word)

cat("Matched words:", nrow(comparison), "\n")
cat("CHILDES words with no CDI match:", length(childes_unmatched), "\n")
print(childes_unmatched)
cat("CDI words with no CHILDES match:", length(cdi_unmatched), "\n")
print(cdi_unmatched)

comparison
```

# Validation Statistics

```{r validationStats}
thresholds <- c("age_above_0.1", "age_above_0.15", "age_above_0.2")

cor_results <- map_dfr(thresholds, function(t) {
  pear <- cor.test(comparison$Estimate, comparison[[t]], method = "pearson")
  spear <- cor.test(comparison$Estimate, comparison[[t]], method = "spearman")
  diff <- comparison$Estimate - comparison[[t]]
  tibble(
    cdi_threshold = t,
    pearson_r   = unname(pear$estimate),
    pearson_p   = pear$p.value,
    spearman_rho = unname(spear$estimate),
    spearman_p   = spear$p.value,
    mean_abs_diff = mean(abs(diff)),
    rmse = sqrt(mean(diff^2))
  )
})

cor_results
```

```{r lmModel}
lm_fit <- lm(Estimate ~ age_above_0.15, data = comparison)
glance(lm_fit)
tidy(lm_fit)
```

# Comparison Plot

```{r comparisonPlot, fig.width=8, fig.height=7}
r_annotation <- sprintf("Pearson r = %.2f, Spearman rho = %.2f",
                         cor_results$pearson_r[cor_results$cdi_threshold == "age_above_0.15"],
                         cor_results$spearman_rho[cor_results$cdi_threshold == "age_above_0.15"])

validation_plot <- ggplot(comparison, aes(x = age_above_0.15, y = Estimate)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", colour = "grey50") +
  geom_errorbar(aes(ymin = Q2.5, ymax = Q97.5), width = 0, colour = "grey70") +
  geom_errorbarh(aes(xmin = age_above_0.1, xmax = age_above_0.2), height = 0, colour = "grey70") +
  geom_point(colour = "steelblue") +
  geom_text_repel(aes(label = word), size = 3, max.overlaps = 30) +
  annotate("text", x = -Inf, y = Inf, label = r_annotation, hjust = -0.05, vjust = 1.5, size = 4) +
  labs(
    x = "CDI onset age (months, proportion producing >= 0.15; whiskers = 0.1-0.2 range)",
    y = "CHILDES age of production (months, Gompertz lag estimate; whiskers = 95% CI)",
    title = "CHILDES growth-curve estimates vs. CDI onset ages"
  ) +
  theme_bw()

validation_plot
```

# Save Outputs

```{r saveOutputs}
write_csv(comparison, "cdi_childes_comparison.csv")
ggsave("cdi_validation_plot.png", validation_plot, width = 8, height = 7, dpi = 150)
```
